Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-14 paper.qmd
Updated Figure10 labels

error_plot_one_curvy_hist_selected <- ggplot(error_df_one_curvy_abs_deselected11, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected11, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, color = "#800026", size = 3) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("b1",
                      position = c(0.95, 0.9),
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))

@@

error_plot_one_curvy_hist <- ggplot(error_df_one_curvy_abs_deselected12, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected12, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, color = "#800026", size = 3) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("a1",
                      position = c(0.95, 0.9),
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))
```

>>>>

error_plot_one_curvy_hist_selected <- ggplot(error_df_one_curvy_abs_deselected11, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected11, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, color = "#800026", size = 3) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("b1",
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))

@@

error_plot_one_curvy_hist <- ggplot(error_df_one_curvy_abs_deselected12, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected12, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, color = "#800026", size = 3) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("a1",
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))
```
